%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Systems Specialist - Platform Application Services} % Job title
    {Squarepoint Capital} % Organization
    {Singapore} % Location
    {Feb. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Subject Matter Expert for On-Prem GitLab Infrastructure (Configuring/Administering)}
        \item {Manage cloud infra (AWS/GCP) using Terraform}
        \item {Developed a solution of monitoring + alerting Terraform config drifts for our cloud projects (Python)}
        \item {Led a major refactoring effort in all terraform repos to keep code DRY and reduce maintainence overhead (Terraform)}
        \item {Enforced various IT security requirements for Cloud by creating reusable, compliant Terraform modules (Terraform)}
        \item {Provide Application Support for Critical Systems on rotational-shift basis}
      \end{cvitems}
    }

  \cventry
    {Software Developer (DevOps)} % Job title
    {} % Organization
    {} % Location
    {Aug. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Config Management for on-prem services with Chef}
        \item {Maintained / Implemented CICD pipelines+libraries+templates (Gitlab CI/ Bamboo)}
        \item {Developed server-side git hook dispatcher for hosted Gitlab (Python)}
        \item {Developed / Maintained alerts and metric dashboards for services (Prometheus/Grafana)}
      \end{cvitems}
    }

  \cventry
    {Associate DevOps Engineer} % Job title
    {GovTech Singapore} % Organization
    {Singapore} % Location
    {Jun. 2021 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed Infrastructure to public cloud (AWS) with IaC tools. (aws/terraform/terragrunt)}
        \item {Implemented multiple process improvements / automation using CI/CD. (GitHub Actions/CodeFresh/python/bash)}
        \item {Contributed to various Front-End engineering tasks for UI improvements and bug fixes. (react/javascript/css/html)}
      \end{cvitems}
    }

  \cventry
    {Summer Technology Analyst - Global Markets Operations Technology} % Job title
    {Bank of America} % Organization
    {Singapore} % Location
    {Jun. 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to a development of a mock system to simulate an external system that our application interface with, reducing cost and increasing testability of said system.}
      \end{cvitems}
    }

  \cventry
    {Industrial Attachment Technology Analyst - Equities Technologies} % Job title
    {} % Organization
    {} % Location
    {Jan. 2020 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated internal applications from an in-house deployment platform to the open-source Ansible for deployments.}
        \item {Built fully automated CI/CD pipelines on TeamCity for deploying applications automatically upon changes made by developers to the application's source code.}
      \end{cvitems}
    }


%---------------------------------------------------------
  % \cventry
  %   {Data Analytics Intern - Regional Business Intelligence} % Job title
  %   {Shopee} % Organization
  %   {Singapore} % Location
  %   {Aug. 2019 - Dec. 2019} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Maintained over 20 scripts that are in production for generating key reports for various stakeholders in the company.}
  %       \item {Led Version Control Software (git) training and material preparation for Regional Business Intelligence department.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  % \cventry
  %   {Research Development Intern - Cyber Security} % Job title
  %   {Acronis} % Organization
  %   {Singapore} % Location
  %   {May. 2019 - Aug. 2019} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Implemented over 30 automated test cases using Python’s pytest framework to ensure the resiliency of the company’s products.}
  %       \item {Maintained Jenkins CI pipelines to automate the triggering for the automated test cases for testing the company’s product as soon as a new build is available to detect bugs at the earliest opportunity.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  % \cventry
  %   {Software Engineering Summer Intern - Global eCommerce Solutions} % Job title
  %   {Pitney Bowes} % Organization
  %   {Tokyo, Japan} % Location
  %   {Jun. 2018 - Aug. 2018} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Spearheaded a project to automate data collection and report generation using Python; improved efficiency by over 40 times.}
  %       \item {Laid out and maintained documentation of the project for future development.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
